Surface Source Extension, Reflection Case

### 2020-01-23 repro/papers/sserefl/paper.tex
finished WRI trans comp

While I have endeavoured to limit mathematical technicalities in this background
presentation, one such technicality intrudes at this point: the
output of the transpose operator $\tS[\kappa]^T$ is nonzero and non-decaying arbitrarily
far in space and in negative time. As will be obvious shortly, this
fact prevents the composition $\tS[\kappa]\tS[\kappa]^T$ from being
well-defined, without some further constraint being imposed on the
domain of $\tS[\kappa]$. The simplest appears to be the assumption
that all plane wave sources act over a limited depth range, $0 \le z
\le z_{\rm max}$. Then the $z$ integrals appearing in the expressions
for $S$ and $\tS$ have limits $[0,z_{\rm max}]$

With this amendment, compute the composition:
\[
  \tS[\kappa]\tS[\kappa]^T\te(\xi,t) = \frac{1}{2}(1-c_0^2\xi^2)^{-1}
\]
\[
  \times 
  \int_0^{z_{\rm max}} dz\, \frac{1}{2}(1-c_0^2\xi^2)^{-1}\te\left(\xi,t' +
    \frac{|z_r-z|}{\tc_0(\xi)}\right)_{t'=t-\frac{|z_r-z|}{\tc_0(\xi)}}
\]
\begin{equation}
  \label{eqn:stmodhompwnorm}
 = \frac{z_{\rm max}}{4}(1-c_0^2\xi^2)^{-2}\te(\xi,t)
\end{equation}

@@

\paragraph{Transmission:} $z_s < z_r$, $\kappa_*$ is smooth and $ = \kappa_0$ for
$z$ near $z_s$, $\ge \kappa_0$ for all $z$, and $>\kappa_0$ for $z$
near $z_r$, Geometric acoustics implies that the solution is given by
the progressing wave expansion [REFERENCE] in terms of the vertical
travel time $\tau(\xi,z_1,z_2)$ and geometric amplitude
$a(\xi,z_1,z_2)$ between depths $z_1$ and $z_2$. The traveltime is given by
\[
\tau(\xi,z_1,z_2) = \int_{z_1}^{z_2}\,dz\, \frac{1}{\tc(\xi,z)}.
\]
I do not give an explicit expression for the amplitude, noting only
that it is smooth in all three variables and positive. The geometric
acoustics approximation of the data is
\begin{equation}
  \label{eqn:geosoltrans}
  \tdl(\xi,t) = a(\xi,z_s,z_r)\wl(t-\tau(\xi,z_s,z_r)).
\end{equation}
The explicit expression \ref{eqn:ptmodhompw} for $\kappa_0$ may be
viewed as a special case of \ref{eqn:geosoltrans}, and gives reference
data for that case:
\begin{equation}
  \label{eqn:analsoltrans}
  \td_{0,\lambda}(\xi,t) =  \tS_p[\kappa_0]\wl(\xi,t)  = \frac{1}{2c_0(1-c_0^2\xi^2)^{1/2}}\wl
                                \left(t-\frac{|z_r-z_s|}{\tc_0(\xi)}\right)
\end{equation}

@@

The gradient of the objective, given in equation \ref{eqn:olspwobj},
is
\[
  \nabla J_{\rm FWI}[\kappa] = D\tS[\kappa]^T(\tS[\kappa]\tw_*-d)
\]

For homogeneous background model $\kappa=\kappa_0$, Appendix \appPlane
develops an explicit expression 
\[
D(\tS_p[\kappa]\tw)_{\kappa=\kappa_0}\delta \kappa(\xi,t) =
  -\frac{1}{2\kappa_0c_0(1-c_0^2\xi^2)^{1/2}} \delta 
  \kappa(z_s) w\left(t - \frac{|z_r-z_s|}{\tc_0(\xi)}\right)
\]
\begin{equation}
\label{eqn:dmodhompwpt}
    + \frac{}{4\kappa_0c_0^2(1-c_0^2\xi^2)} \int \,dz\,\delta 
  \kappa(z) \frac{\partial w}{\partial
    t}\left(t - \frac{|z_s-z|+|z-z_r|}{\tc_0(\xi)}\right)
\end{equation}
The conditions imposed on the transmission configuration imply that
$\delta \kappa(z) = 0$ for $z$ near $z_s$. This constraint implies that
\begin{equation}
  \label{eqn:dmodhompwpt0}
  D(\tS_p[\kappa]\tw)_{\kappa=\kappa_0}\delta \kappa(\xi,t) =
     \frac{}{4\kappa_0c_0^2(1-c_0^2\xi^2)} \int \,dz\,\delta 
  \kappa(z)  \frac{\partial w}{\partial
    t}\left(t - \frac{|z_s-z|+|z-z_r|}{\tc_0(\xi)}\right).
\end{equation}
Thus
\begin{equation}
\label{eqn:dmodhomadj}
D(\tS[\kappa]\tw)_{\kappa=\kappa_0}^T\td(z) =
\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi\,\int\,dt\,
\frac{}{4\kappa_0c_0^2(1-c_0^2\xi^2)}
\frac{\partial w}{\partial
    t}\left(t - \frac{|z_s-z|+|z-z_r|}{\tc_0(\xi)}\right) \td(\xi,t).
\end{equation}

@@

From the second equation in the pair \ref{eqn:sol1d}
\[
  \frac{\partial v}{\partial z}(z,t) = \frac{1}{\kappa_0} f(z,t) 
\]
\begin{equation}
  \label{eqn:sol1ddvdz}
 - \frac{1}{2\kappa_0c_0} \int\, dz_2\, \frac{\partial f}{\partial t}\left(z_2,t - \frac{|z-z_2|}{c_0}\right)
\end{equation}
Thus using the first equations in \ref{eqn:sol1d} and \ref{eqn:dawe1d}, 
\[
  \delta p(z,t) =- \frac{1}{2c_0} \int \, dz_1 \, \delta
  \kappa(z_1)\frac{\partial v}{\partial z}\left(z_1,t - \frac{|z-z_1|}{c_0}\right)
\]
\[
  =-\frac{1}{2\kappa_0c_0} \int \,dz_1\, \delta
  \kappa(z_1) f \left(z_1,t - \frac{|z-z_1|}{c_0}\right)
  \]
\begin{equation}
  \label{eqn:sol1ddp}
  + \frac{1}{4\kappa_0c_0^2} \int\,dz_2 \, \int \,dz_1\,\delta 
  \kappa(z_1) \frac{\partial f}{\partial t}\left(z_2,t - \frac{|z_2-z_1|+|z_1-z|}{c_0}\right)
\end{equation}

>>>>

While I have endeavoured to limit mathematical technicalities in this background
presentation, one such technicality intrudes at this point: the
output of the transpose operator $\tS[\kappa]^T$ is nonzero and non-decaying arbitrarily
far in space and in negative time. As will be obvious shortly, this
fact prevents the composition $\tS[\kappa]\tS[\kappa]^T$ from being
well-defined, without some further constraint being imposed on the
domain of $\tS[\kappa]$. The simplest appears to be the assumption
that all plane wave sources act over a limited depth range, $z_{\rm min} \le z
\le z_{\rm max}$. Then the $z$ integrals appearing in the expressions
for $S$ and $\tS$ have limits $[z_{\rm min},z_{\rm max}]$

With this amendment, compute the composition:
\[
  \tS[\kappa_0]\tS[\kappa_0]^T\te(\xi,t) = \frac{1}{2}(1-c_0^2\xi^2)^{-1}
\]
\[
  \times 
  \int_{z_{\rm min}}^{z_{\rm max}} dz\, \frac{1}{2}(1-c_0^2\xi^2)^{-1}\te\left(\xi,t' +
    \frac{|z_r-z|}{\tc_0(\xi)}\right)_{t'=t-\frac{|z_r-z|}{\tc_0(\xi)}}
\]
\begin{equation}
  \label{eqn:stmodhompwnorm}
 = \frac{z_{\rm max}-z_{\rm min}}{4}(1-c_0^2\xi^2)^{-2}\te(\xi,t) 
\end{equation}

@@

\paragraph{Transmission:} $z_s < z_r$, $\kappa_*$ is smooth and and
differs from $\kappa_0$ only between $z_s$ and $z_r$: that is, $\kappa = \kappa_0$ for
$z < z_s+\epsilon$, $z>z_r-\epsilon$, suitable $\epsilon>0$. To ensure
that the data computed from $\kappa_*$ is distinct from the reference
data computed from $\kappa_0$, also assume that $\kappa \ge \kappa_0$,
and that $\kappa > \kappa_0$ over some subinterval of $[z_s,z_r]$ of
positive length.

Geometric acoustics implies that the solution for $\kappa_*$ is
asymptotic to the first term of the progressing wave expansion
[REFERENCE], which depends on the vertical
travel time $\tau_*(\xi,z_1,z_2)$ and geometric amplitude
$a_*(\xi,z_1,z_2)$ between depths $z_1$ and $z_2$. The traveltime is given by
\[
\tau(\xi,z_1,z_2) = \int_{z_1}^{z_2}\,dz\, \frac{1}{\tc_*(\xi,z)}.
\]
I do not give an explicit expression for the amplitude, noting only
that it is smooth in all three variables and positive.

The geometric
acoustics approximation of the data is
\begin{equation}
  \label{eqn:geosoltrans}
  \tdl(\xi,t) = a(\xi,z_s,z_r)\wl(t-\tau(\xi,z_s,z_r)) + O(\lambda). 
\end{equation}
The explicit expression \ref{eqn:ptmodhompw} for $\kappa_0$ may be 
viewed as a special case of \ref{eqn:geosoltrans}, and gives reference 
data for that case: 
\begin{equation}
  \label{eqn:analsoltrans}
  \td_{0,\lambda}(\xi,t) =  \tS_p[\kappa_0]\wl(\xi,t)  = \frac{1}{2c_0(1-c_0^2\xi^2)^{1/2}}\wl 
                                \left(t-\frac{|z_r-z_s|}{\tc_0(\xi)}\right) 
\end{equation}
The vertical travel time for $\kappa=\kappa_0$ is
\[
  \tau_0(\xi,z_1,z_2) = \frac{z_2-z_1}{\tc_0(\xi)}.
\]
A consequence of the assumptions about the relation between $\kappa_*$
and $\kappa_0$, stated above, is that $\tau_*(\xi,z_s,z_r) <
\tau_0(\xi,z_s,z_r)$ for $|\xi|\le \xi_{\rm max}$.

@@

The gradient of the objective, given in equation \ref{eqn:olspwobj},
is
\begin{equation}
  \label{eqn:fwigrad}
  \nabla J_{\rm FWI}[\kappa] = D\tS_p[\kappa]^T(\tS_p[\kappa]\wl-\tdl)
\end{equation}
The first step in this computation is 
For homogeneous background model $\kappa=\kappa_0$, Appendix \appPlane
develops an explicit expression 
\[
D(\tS_p[\kappa_0]\wl)_{\kappa=\kappa_0}\delta \kappa(\xi,t) =
  -\frac{1}{2\kappa_0c_0(1-c_0^2\xi^2)^{1/2}} \delta 
  \kappa(z_s) \wl\left(t - \frac{|z_r-z_s|}{\tc_0(\xi)}\right)
\]
\begin{equation}
\label{eqn:dmodhompwpt}
    + \frac{1}{4\kappa_0c_0^2(1-c_0^2\xi^2)} \int \,dz\,\delta 
  \kappa(z) \frac{\partial \wl}{\partial
    t}\left(t - \frac{|z_s-z|+|z-z_r|}{\tc_0(\xi)}\right)
\end{equation}
The conditions imposed on the transmission configuration imply that
$\delta \kappa(z) = 0$ for $z$ near $z_s$. This constraint implies that
\begin{equation}
  \label{eqn:dmodhompwpt0}
  D(\tS_p[\kappa]\wl)_{\kappa=\kappa_0}\delta \kappa(\xi,t) =
     \frac{1}{4\kappa_0c_0^2(1-c_0^2\xi^2)} \int \,dz\,\delta 
  \kappa(z)  \frac{\partial \wl}{\partial 
    t}\left(t - \frac{|z_s-z|+|z-z_r|}{\tc_0(\xi)}\right). 
\end{equation}
Furthermore, $\delta \kappa = 0$ for $z>z_r$ as well, which means that
the integral may be restricted to the interval $z_s \le z \le
z_r$. Thus in the range of integration, $|z_s-z| + |z_r-z|=z_r-z_s$
whence equation \ref{eqn:dmodhompwpt0} may be rewritten as
\begin{equation}
  \label{eqn:dmodhompwpt1}
  D(\tS_p[\kappa]\wl)_{\kappa=\kappa_0}\delta \kappa(\xi,t) =
     \frac{1}{4\kappa_0c_0^2(1-c_0^2\xi^2)} \frac{\partial \wl}{\partial 
    t}\left(t - \frac{z_r-z_s}{\tc_0(\xi)}\right) \left(\int_{z_s}^{z_r} \,dz\,\delta 
  \kappa(z) \right). 
\end{equation}
Note that the linearized transmission seismogram is only sensitive to
the average of $\delta \kappa$ between $z_s$ and $z_r$, which is in
turn proportional by a $\xi$-dependent factor to the perturbation in
travel time between source and receiver. Accordingly, the adjoint of
the linearized forward map outputs a $z$-independent bulk modulus perturbation:
\begin{equation}
\label{eqn:dmodhompwptadj}
D(\tS[\kappa]\wl)_{\kappa=\kappa_0}^T\td(z) =
\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi\,\int\,dt\,
\frac{1}{4\kappa_0c_0^2(1-c_0^2\xi^2)}
\frac{\partial w}{\partial
    t}\left(t - \frac{z_r-z_s}{\tc_0(\xi)}\right) \td(\xi,t).
\end{equation}

To compute the gradient \ref{eqn:fwigrad} at the homogeneous bulk
modulus $\kappa_0$, recall that the target data is
given by \ref{eqn:geosoltrans}, and the trial data for
$\kappa=\kappa_0$ by \ref{eqn:analsoltrans}. Insert these into the
right hand side of the identity \ref{eqn:fwigrad}:
\[
  \nabla J_{\rm FWI}[\kappa_0](z) =
  D(\tS[\kappa]\wl)_{\kappa=\kappa_0}^T(a_0\wl(t-\tau_0)
  -a\wl(t-\tau))(z) + O(\lambda)
\]
\[
=  \int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi\,\int\,dt\,
\frac{1}{4\kappa_0c_0^2(1-c_0^2\xi^2)}
\frac{\partial \wl}{\partial
    t}(t - \tau_0(\xi,z_s,z_r))
  \left(a_0(\xi,z_s,z_r)\wl(t-\tau_0(\xi,z_s,z_r) )\right.
\]
\[
-
\left.  a(\xi,z_s,z_r)\wl(t-\tau(\xi,z_s,z_r))\right) + O(\lambda)
\]
\[
  = \int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi\,
\frac{1}{4\kappa_0c_0^2(1-c_0^2\xi^2)}\left[a_0(\xi,z_s,z_r) \int \,
  dt \, \left(\frac{\partial \wl}{\partial t}\wl  \right)
  (t-\tau_0(\xi,z_s,z_r))
\right.
\]
\[
  \left.
- a(\xi,z_s,z_r) \int\,dt\,\frac{\partial \wl}{\partial t} 
  (t-\tau_0(\xi,z_s,z_r)) \wl(t-\tau(\xi,z_s,z_r)\right] + O(\lambda)
\]
The first of the two $t$ integrals vanishes because the integrand is
an exact derivative (of $\wl^2/2$) . The second vanishes when
$\lambda$ is small enough that the support of $\wl$ is smaller than
half of $\tau_0(\xi,z_s,z_r)-\tau(\xi,z_s,z_r)$ for $\xi$ in the
interval of integration. Therefore we conclude that
\[
  \nabla J_{\rm FWI}[\kappa_0] = O(\lambda)
\]
as stated in the last section.

\subsection{WRI, Transission Configuration}
In this configuration, $z_{\rm min}=z_s < z_r=z_{\rm max}$ and
\begin{equation}
  \label{eqn:writransupp}
  \mbox{supp }\tf \subset [-\xi_{\rm max},\xi_{\rm max}]\times
  [z_s,z_r]\times \bR.
\end{equation}
Recall that (equation \ref{eqn:wripwiva1} with $w_*=\wl$)
\begin{equation}
  \label{eqn:wripwiva1}
  J_{\rm WRI}[\kappa]   = \frac{1}{2}\langle \td -
  \tS_p[\kappa]\wl, (\tS[\kappa]\tS[\kappa]^T)^{-1}( \td -
  \tS[\kappa]\wl) \rangle  
\end{equation} 
Thus
\[
  D J_{\rm WRI}[\kappa]\delta \kappa|_{\kappa=\kappa_0}   =
  DJ_1[\kappa]\delta \kappa|_{\kappa=\kappa_0} +
  DJ_2[\kappa]\delta \kappa|_{\kappa=\kappa_0},
\]
in which
\[
  J_1[\kappa]   = \frac{1}{2}\langle \td -
  \tS_p[\kappa]\wl, (\tS[\kappa_0]\tS[\kappa_0]^T)^{-1}( \td -
  \tS_p[\kappa]\wl) \rangle 
\]
and
\[
 J_2[\kappa] =  \frac{1}{2}\langle \td -
  \tS_p[\kappa_0]\wl, (\tS[\kappa]\tS[\kappa]^T)^{-1}( \td -
  \tS_p[\kappa_0]\wl) \rangle
\]
Recall that 
\[
  \tS[\kappa_0]\tS[\kappa_0]^T\te(\xi,t) = \frac{z_{\rm max}-z_{\rm min}}{4}(1-c_0^2\xi^2)^{-2}\te(\xi,t).
\]
(equation \ref{eqn:stmodhompwnorm}). Thus $J_1$ is a statically
eqweighted version of $J_{\rm FWI}$. The estimation of $D J_{\rm
  FWI}[\kappa]\delta \kappa|_{\kappa=\kappa_0}$ follows exactly the
same pattern as the 
estimation of $D J_{\rm
  FWI}[\kappa]\delta \kappa|_{\kappa=\kappa_0}$ in the last section,
and yields
\begin{equation}
  \label{eqn:j1est}
  \nabla J_1[\kappa_0] = O(\lambda).
\end{equation}

To estimate $\nabla J_2[\kappa_0]$, abbreviate
\[
  \te=\td -
  \tS_p[\kappa_0]\wl 
\]
and note that
\[
  DJ_2[\kappa]\delta \kappa|_{\kappa=\kappa_0} = -
  \frac{1}{2}\langle \te,
  (\tS[\kappa_0]\tS[\kappa_0]^T)^{-1}\left((D\tS[\kappa]\delta
  \kappa)_{\kappa=\kappa_0}\tS[\kappa_0]^T\right.
\]
\[
  \left.+\tS[\kappa_0](D\tS[\kappa]\delta
  \kappa)_{\kappa=\kappa_0}^T\right) (\tS[\kappa_0]\tS[\kappa_0]^T)^{-1} \te\rangle
\]
\begin{equation}
  \label{eqn:dj2}
 = -\langle \te,(\tS[\kappa_0]\tS[\kappa_0]^T)^{-1}
  ((D\tS[\kappa]\delta
  \kappa)_{\kappa=\kappa_0}\tS[\kappa_0]^T)
  (\tS[\kappa_0]\tS[\kappa_0]^T)^{-1}\te\rangle
\end{equation}
Recall that $\mbox{supp }(\tf) \subset \{z_s \le z \le
z_r\}$, that is, the domain of $\tS$ is actually
$L^2([-\xi_{\rm max},\xi_{\rm max}] \times [z_s,z_r] \times
\bR)$. Injection of this domain into $L^2(\bR^3)$ is equivalent to
placing limits on the various integrals that appear in the definitions
of $\tS$ and related operators. For the adjoint, the dual projection
is part of the definition:
\begin{equation}
  (\tS[\kappa_0]^T\te)(\xi,z,t)=\frac{1}{2}(1-c_0^2\xi^2)^{-1}\te\left(\xi,t +
    \frac{|z_r-z|}{\tc_0(\xi)}\right), \,|\xi|\le \xi_{rm max}, z_s
  \le z \le z_r, \, =0 \mbox{ else}.
\end{equation}
(equation \ref{eqn:stmodhompwtrans}). From equation \ref{eqn:dmodhomst1app},
\[
  D(\tS[\kappa_0]\tf)_{\kappa=\kappa_0}\delta \kappa(\xi,t) =
  -\frac{1}{2\kappa_0c_0(1-c_0^2\xi^2)^{1/2}}\int \,dz_1\, \delta 
  \kappa(z_1) \tf \left(\xi,z_1,t - \frac{|z_r-z_1|}{\tc_0(\xi)}\right)
\]
\[
    + \frac{1}{4\kappa_0c_0^2(1-c_0^2\xi^2)} \int\,dz_2 \, \int \,dz_1\,\delta 
  \kappa(z_1)  \frac{\partial \tf}{\partial
    t}\left(\xi,z_2,t - \frac{|z_2-z_1|+|z_1-z_r|}{\tc_0(\xi)}\right)
\]
So
\[
 ( D\tS[\kappa]\delta \kappa) \tS^T[\kappa]\te(\xi,t) =
  -\frac{1}{4\kappa_0c_0}(1-c_0^2\xi^2)^{-3/2} \te(\xi,t)
  \int_{z_s}^{z_r}\,dz\,\delta \kappa (z)
\]
\begin{equation}
  \label{eqn:dmodhompwst2}
     + \frac{1}{8\kappa_0c_0^2(1-c_0^2\xi^2)^2} \int_{z_s}^{z_r}\,dz_2 \, \int_{z_s}^{z_r} \,dz_1\,\delta 
  \kappa(z_1)  \frac{\partial \te}{\partial
    t}\left(\xi,t - \frac{|z_2-z_1|+|z_1-z_r|-|z_r-z_2|}{\tc_0(\xi)}\right)
\end{equation}
The integral in the secont term splits naturally into the subdomains
\begin{eqnarray*}
 z_s \le z_2 \le z_1 \le z_r & \Rightarrow &
                                            |z_2-z_1|+|z_1-z_r|-|z_r-z_2|
                                            = z_1-z_2 + z_r-z_1 -
                                           ( z_r-z_2) = 0\\
z_s \le z_1 \le z_2\le z_r  & \Rightarrow
                                          &|z_2-z_1|+|z_1-z_r|-|z_r-z_2|
                                            = z_2-z_1 + z_r-z_1 -
                                            (z_r-z_2) = 2(z_2-z_1)
\end{eqnarray*}
So
\[
  \int_{z_s}^{z_r} \,dz_2\, \frac{\partial \te}{\partial 
    t}\left(\xi,t -
    \frac{|z_2-z_1|+|z_1-z_r|-|z_r-z_2|}{\tc_0(\xi)}\right) 
\]
\[
  = \int_{z_1}^{z_r} \,dz_2\, \frac{\partial
    \te}{\partial t}\left(\xi,t-\frac{2(z_2-z_1)}{\tc_0(\xi)}\right)
  + (z_1-z_s) \frac{\partial
    \te}{\partial t}(\xi,t)
\]
\[
=-\frac{\tc_0}{2}\int_{z_1}^{z_r} \,dz_2\, \frac{\partial}{\partial z_2}\te\left(\xi,t-\frac{2(z_2-z_1)}{\tc_0(\xi)}\right)
  + (z_1-z_s) \frac{\partial
    \te}{\partial t}(\xi,t)
\]
\[
  = -\frac{\tc_0}{2}\left(\te\left(\xi,t-\frac{2(z_r-z_1)}{\tc_0(\xi)}\right)-\te(\xi,t)\right)
    + (z_1-z_s) \frac{\partial
    \te}{\partial t}(\xi,t)
\]
so 
\[
  ( D\tS[\kappa]\delta \kappa) \tS^T[\kappa]\te(\xi,t) =
  \frac{1}{4\kappa_0c_0}\left(\frac{1}{4}(1-c_0^2\xi^2)^{-5/2}- (1-c_0^2\xi^2)^{-3/2}\right) \te(\xi,t)
  \int_{z_s}^{z_r}\,dz\,\delta \kappa (z)
\]
\begin{equation}
  \label{eqn:dmodhompwst3}
     + \frac{1}{8\kappa_0c_0^2(1-c_0^2\xi^2)^2}
     \int_{z_s}^{z_r}\,dz_1\,\delta\kappa(z_1) \left((z_1-z_s) \frac{\partial
    \te}{\partial t}(\xi,t) -\frac{\tc_0}{2}\te\left(\xi,t-\frac{2(z_r-z_1)}{\tc_0(\xi)}\right)\right)
\end{equation}
Therefore 
\[
  DJ_2[\kappa]\delta \kappa|_{\kappa=\kappa_0} = \left(\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi \,W_0(\xi)
  \int\,dt\, \te(\xi,t)^2\right)\int_{z_s}^{z_r}\,dz\,\delta \kappa
\]
\[
     -\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi\,W_1(\xi)\int\,dt\, \int_{z_s}^{z_r}\,dz_1\,\delta\kappa(z_1) \left((z_1-z_s) \te(\xi,t)\frac{\partial 
         \te}{\partial t}(\xi,t) \right.
     \]
\begin{equation}
  \label{eqn:dj2e1}
 \left.    -\frac{\tc_0}{2}\te(\xi,t)\te\left(\xi,t-\frac{2(z_r-z_1)}{\tc_0(\xi)}\right)\right)
\end{equation}
In the right-hand side of equation \ref{eqn:dj2e1}, $W_0$ and $W_1$
are functions of $\xi$, parametrized by $\kappa_0$ and $\rho_0$. They
have no depedence on the target model $\kappa_*,\rho_*$ used to
generate the target data $d$.

Note that the first summand under the integral sign in the second term
integrates to zero in $t$, as it is an exact derivative of a smooth
compactly supported function. Therefore combining equations
\ref{eqn:j1est} and \ref{eqn:dj2e1} and the definition of the formal
or $L^2$ gradient, obtain
\[
  \nabla J_{\rm WRI}[\kappa_0](z) = \left(\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi \,W_0(\xi)
    \int\,dt\, \te(\xi,t)^2\right) {\bf 1}_{[z_s,z_r]}(z)
\]
\begin{equation}
  \label{eqn:gradwri1}
  +\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi\,W_2(\xi)\int\,dt\, 
  \te(\xi,t)\te\left(\xi,t-\frac{2(z_r-z)}{\tc_0(\xi)}\right) + O(\lambda)
\end{equation}
in which $W_2 = (\tc_0/2)W_1$.

The inner ($t$) integral in the second term on the RHS of
\ref{eqn:gradwri1} is the autocorrelation of $\te$ at lag
$2(z_r-z)/\tc_0(\xi)$. Introducing the Fourier transform $\hat{\te}$
of $\te$ in $t$,
\[
  \nabla J_{\rm WRI}[\kappa_0](z) = \left(\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi \,W_0(\xi)
    \int\,dt\, \te(\xi,t)^2\right) {\bf 1}_{[z_s,z_r]}(z)
\]
\begin{equation}
  \label{eqn:gradwri2}
  +\frac{1}{2\pi}\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi\,W_2(\xi)\int\,d\omega\, 
  |\hat{\te}(\xi,\omega)|^2e^{-i\omega\frac{2(z_r-z)}{\tc_0(\xi)}} + O(\lambda)
\end{equation}
Recall that
\[
  \te=\tdl -
  \td_{0,\lambda}
\]
and
\begin{equation}
  \label{eqn:geosoltrans1}
  \tdl(\xi,t) = a(\xi,z_s,z_r)\wl(t-\tau(\xi,z_s,z_r)) + O(\lambda). 
\end{equation}
The explicit expression \ref{eqn:ptmodhompw} for $\kappa_0$ may be 
viewed as a special case of \ref{eqn:geosoltrans}, and gives reference 
data for that case: 
\begin{equation}
  \label{eqn:analsoltrans1}
  \td_{0,\lambda}(\xi,t) =  \tS_p[\kappa_0]\wl(\xi,t)  = a_0(\xi,z_s,z_r)\wl 
  \left(t-\frac{|z_r-z_s|}{\tc_0(\xi)}\right) 
\end{equation}
where $a_0$ is given in \ref{eqn:anasoltrans}. So
\[
  \te(\xi,t) = \tdl(\xi,t)-\td_{0,\lambda}(\xi,t) =
  \frac{1}{\sqrt{\lambda}}\te_1\left(\xi,\frac{t}{\lambda}\right) + O(\lambda),
\]
in which
\begin{equation}
  \label{eqn:e1def}
  \te_1 = \td_1 -\td_{0,1}.
\end{equation}
In terms of the Fourier transform,
\[
  \hat{\te}(\xi,\omega) = \sqrt{\lambda}\hat{\te}_1(\xi,\lambda\omega)
  + O(\lambda)
\]

Calculating the rate of change of traveltime between $z_s$ and $z_r$:
\[
  \delta \int_{z_s}^{z_r}\,\frac{1}{\tc}|_{\kappa=\kappa_0} =
  -\frac{\rho \tc_0}{\kappa_0^2} \int_{z_s}^{z_r}\,\delta \kappa
\]
The rate at $\kappa=\kappa_0$ in the direction $\delta \kappa =
-\nabla J_{\rm WRI}(\kappa_0)$ is therefore
\[
  = \left[(z_r-z_s) \left(\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi \, \frac{\rho \tc_0(\xi)}{\kappa_0^2} W_0(\xi)
    \int\,dt\, \te(\xi,t)^2\right)\right.
\]
\[
 \left. +\frac{1}{2\pi}\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi\,W_2(\xi)\int\,d\omega\, 
  |\hat{\te}(\xi,\omega)|^2 \int_{z_s}^{z_r}\, dz\,e^{-i\omega\frac{2(z_r-z)}{\tc_0(\xi)}} \right]+ O(\lambda)
\]
(all integrals are absolutely convergent hence can be interchanged)
\[
  = \left[(z_r-z_s) \left(\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi \, \frac{\rho \tc_0(\xi)}{\kappa_0^2} W_0(\xi) 
    \int\,dt\, \te(\xi,t)^2\right)\right. 
\]
\[
 \left. +\frac{1}{2\pi}\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi\, \frac{\rho \tc_0(\xi)}{\kappa_0^2} W_2(\xi)\int\,d\omega\, 
  \lambda|\hat{\te}_1(\xi,\lambda\omega)|^2 \int_{z_s}^{z_r}\, dz\,e^{-i\omega\frac{2(z_r-z)}{\tc_0(\xi)}} \right]+ O(\lambda) 
\]
\[
  = \left[(z_r-z_s) \left(\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi \, \frac{\rho \tc_0(\xi)}{\kappa_0^2} W_0(\xi) 
    \int\,dt\, \te(\xi,t)^2\right)\right. 
\]
\[
 \left. +\frac{1}{2\pi}\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi\, \frac{\rho \tc_0(\xi)}{\kappa_0^2} W_2(\xi)\lambda\int\,\frac{d\sigma}{\sigma}\, 
  |\hat{\te}_1(\xi,\sigma)|^2 \int_{z_s}^{z_r}\, dz\,e^{-i\sigma\frac{2(z_r-z)}{\lambda\tc_0(\xi)}} \right]+ O(\lambda) 
\]
\[
  = \left[(z_r-z_s) \left(\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi \, \frac{\rho \tc_0(\xi)}{\kappa_0^2} W_0(\xi) 
    \int\,dt\, \te(\xi,t)^2\right)\right. 
\]
\[
 \left. +\frac{1}{2\pi}\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi\, \frac{\rho \tc_0(\xi)}{\kappa_0^2} W_2(\xi)\lambda\int\,\frac{d\sigma}{\sigma}\, 
   |\hat{\te}_1(\xi,\sigma)|^2 \int_{z_s}^{z_r}\,
   dz\,\frac{\lambda\tc_0(\xi)}{2i\sigma}\frac{\partial}{\partial
       z}e^{-i\sigma\frac{2(z_r-z)}{\lambda\tc_0(\xi)}} \right]+ O(\lambda) 
\]
\[
  = \left[(z_r-z_s) \left(\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi \, \frac{\rho \tc_0(\xi)}{\kappa_0^2} W_0(\xi) 
    \int\,dt\, \te(\xi,t)^2\right)\right. 
\]
\[
 \left. +\frac{\lambda^2}{2\pi}\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi\, \frac{\rho \tc_0(\xi)^2}{\kappa_0^2} W_2(\xi)\int\,d\sigma\, 
   |\frac{\hat{\te}_1(\xi,\sigma)}{i\sigma}|^2 \frac{1}{2i}(1-e^{-i\sigma\frac{2(z_r-z_s)}{\lambda\tc_0(\xi)}}) \right]+ O(\lambda) 
\]

In view of the relation \ref{eqn:e1def}, the assumption that $w_1$ is
the derivative of a $C_0^{\infty}$ primitive, and the uniform boundedness of
the other factors in the integral with respect to $\lambda$, it
follows finally that the rate is
\begin{equation}
  \label{eqn:dttwri}
  =(z_r-z_s) \left(\int_{-\xi_{\rm max}}^{\xi_{\rm max}}\,d\xi \, \frac{\rho \tc_0(\xi)}{\kappa_0^2} W_0(\xi) 
    \int\,dt\, \te(\xi,t)^2\right) + O(\lambda)
\end{equation}

@@

From \ref{eqn:sol1dv}
\[
  \frac{\partial v}{\partial z}(z,t) = \frac{1}{\kappa_0} f(z,t) 
\]
\begin{equation}
  \label{eqn:sol1ddvdz}
 - \frac{1}{2\kappa_0c_0} \int\, dz_2\, \frac{\partial f}{\partial t}\left(z_2,t - \frac{|z-z_2|}{c_0}\right)
\end{equation}
Thus using equation \ref{eqn:sol1dp} and \ref{eqn:dawe1d}, 
\[
  \delta p(z,t) =- \frac{1}{2c_0} \int \, dz_1 \, \delta
  \kappa(z_1)\frac{\partial v}{\partial z}\left(z_1,t - \frac{|z-z_1|}{c_0}\right)
\]
\[
  =-\frac{1}{2\kappa_0c_0} \int \,dz_1\, \delta
  \kappa(z_1) f \left(z_1,t - \frac{|z-z_1|}{c_0}\right)
  \]
\begin{equation}
  \label{eqn:sol1ddp}
  + \frac{1}{4\kappa_0c_0^2} \int\,dz_2 \, \int \,dz_1\,\delta 
  \kappa(z_2) \frac{\partial f}{\partial t}\left(z_1,t - \frac{|z_1-z_2|+|z_2-z|}{c_0}\right)
\end{equation}

A convenient check on this calculation is available for constant
$\delta \kappa = \delta \kappa_0$. Directly perturb the RHS of equation 
\ref{eqn:sol1dp}, to obtain
\[
  \delta p(z,t) = -\frac{\delta c_0}{2 c_0^2} \int
  \,dz_1\,f\left(z_1,t-\frac{|z-z_1|}{c_0}\right)
  +\frac{\delta c_0}{2c_0^3}\int
  \,dz_1\,\frac{\partial f}{\partial
